---
title: "CodeR"
author: "Nabil"
date: "25 September 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Project 1 week 2 : ReproductibleResearch

This is my submission for project 1 in the 5th Course of the 'Data Science: Foundations using R Specialization'.
For more details see the url : <https://www.coursera.org/specializations/data-science-foundations-r>.

Instructions to do this project are here <https://github.com/rdpeng/RepData_PeerAssessment1>


## BEGIN
```{r}
#Import library
# Dont forget to install.packages before the first time
library(data.table)
library(ggplot2)
```

### Loading data
```{r}
fileUrl <- "https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"
tmp<-paste(getwd(), 'act.zip', sep='/')
download.file(fileUrl, destfile = tmp, method = "curl")
unzip("act.zip", exdir = "data")
if (file.exists(tmp)) file.remove(tmp)

DT <- data.table::fread(input = "data/activity.csv")
```

### preprocessing
```{r}
head(DT)
```

```{r}
data<-aggregate(DT$steps, by = list(DT$date), FUN=sum)
names(data)<-c("date", "steps")
head(data)
```

### **1.** Make a histogram of the total number of steps taken each day
```{r}
ggplot(data, aes(x = steps)) +
  geom_histogram(fill = "salmon") +
  labs(title = "Daily Steps", x = "Days", y = "Frequency")
```

### **2.** Calculate and report the mean and median total number of steps taken per day
```{r}
meandANDmedian<-cbind(aggregate(DT$steps, by = list(DT$date),
                    na.rm=TRUE, FUN=median),
          aggregate(DT$steps, by = list(DT$date),
                    FUN=mean)[,"x"])
names(meandANDmedian)<-c("date","mean_st","median_st")
head(meandANDmedian, 10)
```

### What is the average daily activity pattern?
#### 1. Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
#### 2. Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?


.
You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
